Untitled

### 2017-02-03 Manuscript/Manuscript using actual data.Rmd

age_cod_results <-rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_1.csv"),
                        read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_2.csv"),
                        read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_3.csv"))

age_cod_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_1.csv"),
                         read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_2.csv"),
                         read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_3.csv"))

age_decomp_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_3.csv"))

BlackWhite_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_3.csv"))

cod_decomp_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_3.csv"))
```

@@

```{r addvar_State_abbreviation, echo=FALSE}
BlackWhite_results <- BlackWhite_results %>% mutate(stabbrs = factor(state,  
                                                                     labels = c("AL", "AZ", "AR", "CA",
                                                                                "CO", "CT", "DE", "DC",
                                                                                "FL", "GA", "IL", "IN")))
                                      # labels = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "DC",
                                      #            "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", 
                                      #            "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", 
                                      #            "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", 
                                      #            "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", 
                                      #            "VT", "VA", "WA", "WV", "WI", "WY")))

@@

```{r figure5, fig.align="center", fig.height=4, fig.width=9, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_line(aes(y = LE_black, col = state), lty=2) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +           
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), aes(label = stabbrs), check_overlap = T, size = 2.5) +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), aes(label = stabbrs, y = LE_black), check_overlap = T, size = 2.5))

@@

```{r figure6a, fig.align="center", fig.height=4, fig.width=9, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_line(aes(y = LE_black, col = state), lty=2) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +           
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), aes(label = stabbrs), check_overlap = T, size = 2.5) +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), aes(label = stabbrs, y = LE_black), check_overlap = T, size = 2.5))

>>>>

age_cod_results <-rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_1.csv"),
                        read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_2.csv"),
                        read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_3.csv"),
                        read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_4.csv"))

age_cod_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_1.csv"),
                         read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_2.csv"),
                         read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_3.csv"),
                         read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_set_4.csv"))

age_decomp_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_3.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_set_4.csv"))

BlackWhite_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_3.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_set_4.csv"))

cod_decomp_results <- rbind(read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_1.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_3.csv"),
                            read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_set_4.csv"))
```

@@

```{r addvar_State_abbreviation, echo=FALSE}
BlackWhite_results <- BlackWhite_results %>% mutate(stabbrs = factor(state,  
                                                                     labels = c("AL", "AZ", "AR", "CA",
                                                                                "CO", "CT", "DE",
                                                                                "FL", "GA", "IL", "IN",
                                                                                "IA", "KS", "KY", "LA",
                                                                                "DC")))
                                      # labels = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "DC",
                                      #            "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", 
                                      #            "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", 
                                      #            "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", 
                                      #            "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", 
                                      #            "VT", "VA", "WA", "WV", "WI", "WY")))

@@

```{r figure5, fig.align="center", fig.height=4, fig.width=11, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

ggplotly(ggplot(subset(BlackWhite_results, sex == "Male"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Male"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

@@

```{r figure6a, fig.align="center", fig.height=4, fig.width=9, echo=F}
ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_white, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_white_lcl, ymax = LE_white_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))

ggplotly(ggplot(subset(BlackWhite_results, sex == "Female"), aes(y=LE_black, x = year)) + 
           geom_vline(aes(xintercept = 1983), col = "#636363", lwd = 0.5) +
           geom_vline(aes(xintercept = 1993), col = "#636363", lwd = 0.5) +
           geom_ribbon(aes(ymin = LE_black_lcl, ymax = LE_black_ucl, fill = state), alpha=0.25) +
           geom_line(aes(col = state)) +
           facet_wrap( ~ Census_Region) +
           ylab("Life expectancy (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite_results, year == 2013 & sex == "Female"), 
                     aes(label = stabbrs), check_overlap = T, size = 2.5))
